Modelling last glacial cycle ice dynamics in the Alps

### 2018-07-31 articles/cycle/alps-cycle.tex
Update author list and affiliations.

\Author[1]{Julien}{Seguinot}
\Author[1]{Guillaume}{Jouvet}
\Author[1]{Matthias}{Huss}
\Author[1]{Martin}{Funk}
\Author[2]{Susan}{Ivy-Ochs}
\Author[3]{Frank}{Preusser}

\affil[1]{Laboratory of Hydraulics, Hydrology and Glaciology,
          ETH Zürich, Switzerland}
\affil[2]{Laboratory of Ion Beam Physics, ETH Zürich, Switzerland}
\affil[3]{Institute of Earth and Environmental Sciences,
          University of Freiburg, Germany}

>>>>

\Author[1,2]{Julien}{Seguinot}
\Author[3]{Susan}{Ivy-Ochs}
\Author[1]{Guillaume}{Jouvet}
\Author[1]{Matthias}{Huss}
\Author[1]{Martin}{Funk}
\Author[4]{Frank}{Preusser}

\affil[1]{Laboratory of Hydraulics, Hydrology and Glaciology,
          ETH Zürich, Switzerland}
\affil[2]{Arctic Research Center, Hokkaido University, Sapporo, Japan}
\affil[3]{Laboratory of Ion Beam Physics, ETH Zürich, Switzerland}
\affil[4]{Institute of Earth and Environmental Sciences,
          University of Freiburg, Germany}
